ManuscriptPURFits

### 2024-02-28 Code/ManuscriptPURFits.Rmd
Fixed legend for blue vs. red PUR plot. Need to remove linetype from WL and Photoperiod legend. Ask Naaman for help

  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1) +

@@

  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +

@@

  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +

@@

 guides(linetype = guide_legend(order = 1),

@@

        legend.key.size = unit(2, 'cm'), #change legend key size

@@

# This labels each pane with a letter but turns of the facet labels
# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

@@

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450), linetype = "solid", show.legend = T) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660) , linetype = "solid") +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450) , linetype = "solid") +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660) , linetype = "solid") +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450), show.legend = T) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660)) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660) , linetype = "solid")+
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450) , linetype = "solid")+
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 450)) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660)) +

@@

  scale_colour_manual(values = MCMIXColours, labels = c(660, 450)) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Significantly different", "Not significantly different")) +

@@

 guides(linetype = "none",
        # linetype = guide_legend(nrow = 1),

@@

        legend.key.size = unit(0.2, 'cm'), #change legend key size

@@

       linetype = "ANOVA"

>>>>

  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 0.01, alpha = 5, show.legend = F) +

@@

  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", show.legend = F, data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +

@@

  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +

@@

 guides(
   linetype = guide_legend(order = 1),

@@

        legend.key.size = unit(1.8, 'cm'), #change legend key size

@@

@@

  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(WL)), size = 1, show.legend = T) +
# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +
# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Data_all_WL)), size = 1, show.legend = F) +

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450), linetype = "solid", show.legend = F) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660) , linetype = "solid", show.legend = F) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450) , linetype = "solid", show.legend = F) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660) , linetype = "solid", show.legend = F) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450), show.legend = F) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660), show.legend = F) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660) , linetype = "solid", show.legend = F)+
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450) , linetype = "solid", show.legend = F)+
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 450), show.legend = F) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660), show.legend = F) +

@@

  scale_colour_manual(values = MCMIXColours, labels = c("660 nm", "450 nm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("p value < 0.05", "p value > 0.05")) +

@@

 guides(
   linetype = guide_legend(order = 1),
        fill = "none") +

@@

        legend.key.size = unit(1.8, 'cm'), #change legend key size

@@
